The Concurrent Calculi Formalisation Benchmark

### 2024-02-19 short-paper/short-paper.tex
revision of the penultimate paragraph of intro

While results about concurrent
formalisms have already been mechanised (as we will discuss further
below), our experience is that choosing appropriate mechanisation
techniques and tools remains a significant challenge and that the
trade-offs are not well understood.  This often leads researchers
toward a trial-and-error approach, resulting in sub-optimal solutions,
wasted mechanisation effort, and techniques and results that are hard
to reuse. For example, the authors in~\cite{Cruz-Filipe2021b} note that the high-level parts of
mechanised proofs closely resemble the informal ones, and that the
main challenge lies in getting the foundations right.

Our benchmark problems (detailed in \cref{app:challenges}) centre around three key aspects that frequently pose challenges when mechanising concurrency theory: \emph{linearity}, \emph{scope extrusion}, and \emph{coinductive reasoning}.
Mechanisations must often address several of these
aspects at the same time; however, we see the combination of
techniques as a next step beyond the scope of this challenge, as
discussed further in \Cref{sec:going-beyond}.
Our benchmark challenges are based on process calculi, as these provide a simple but
realistic showcase of common issues encountered during mechanisation efforts.
While the three highlighted aspects are not the sole sources of difficulties, they emerge in most mechanisations of concurrency theory.

>>>>

While results about concurrent
formalisms have already been mechanised (as we will discuss further
below), our experience is that choosing appropriate mechanisation
techniques and tools remains a significant challenge and that the
trade-offs are not well understood.  This often leads researchers
toward a trial-and-error approach, resulting in sub-optimal solutions,
wasted mechanisation effort, and techniques and results that are hard
to reuse. For example, the authors in~\cite{Cruz-Filipe2021b} note that the high-level parts of
mechanised proofs closely resemble the informal ones, while the
main challenge lies in getting the foundations right.

Our benchmark problems (detailed in \cref{app:challenges}) consider
\emph{in isolation} three key aspects that frequently pose challenges
when mechanising concurrency theory: \emph{linearity}, \emph{scope
  extrusion}, and \emph{coinductive reasoning}.  Mechanisations must
often address several of these aspects at the same time; however, we
see the combination of techniques as a next
step%beyond the scope of this challenge
, as discussed further in \Cref{sec:going-beyond}.  Our benchmark
challenges are based on process calculi, as these provide a simple but
realistic showcase of common issues encountered during mechanisation
efforts.
% While the three highlighted aspects are not the sole sources of difficulties, they emerge in most mechanisations of concurrency theory.
